Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-11-28 manuscript/manuscript.tex
Edit in determination of D and delta

\citet{Uieda2016} compared the numerical integration of homogeneous density tesseroids
with the analytical solution of a spherical shell \citep{Mikuska2006,Grombein2013} in
order to obtain default values for the distance-size ratio $D$.
We will follow this idea but for our needs the spherical shell must
have the same density function of radius as our tesseroid model.
Analytical solutions for a variable density spherical shell are not present in the
literature and so they must be obtained first.
We derive the expressions for the gravitational fields of spherical shells with linear
and exponential density functions of radius in Appendix \ref{sec:shell}.

>>>>

\citet{Uieda2016} compared the numerical integration of homogeneous density tesseroids
with the analytical solution of a spherical shell \citep{Mikuska2006,Grombein2013} in
order to obtain default values for the distance-size ratio $D$.
We will follow this idea but for our needs the spherical shell must
have the same density function of radius as our tesseroid model.
\citet{Lin2018} show the analytical solution of the gravitational potential generated by
a spherical shell with linear density in the radial coordinate.
We derive an expression for such gravitational potential in case the spherical shell has
an arbitrary density function in depth (Eq. \ref{eq:shell-pot} in Appendix
\ref{sec:shell}), and obtained the expressions in case of linear and exponential
density.
